Visualization of [fulle name] Fractional Integrals

### 2019-04-26 fractional/CMJ style files/article-template.tex
added a new paragraph

Lets clarify the above by working through a detailed example. If we set the value of $\alpha$ to $\frac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
\begin{equation}
\int_{a_{10}^{\frac{4}{5}}(y)}^{b_{10}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
\end{equation}
Let $R_{10}^{\frac{4}{5}}$ denote the region which is bounded by the $x$-axis, the function $f(\tau)$ and the function $b_{10}^{\frac{4}{5}}(y)$. The region $R_{10}^{\frac{4}{5}}$ is depicted and labelled in the right-most panel of Figure.~\ref{??}. We are now in a position to assign a geometric 
interpretaion to Eq.~\eqref{}. We can approximate the area of $R_{10}^{\frac{4}{5}}$ by summing together the area of $n$ non-rectangular integration strips of the same width that inscribe $R_{10}^{\frac{4}{5}}$. The only resctriction being: the sides of these non-rectangualar integration strips have to be translations of $b_{10}^{\frac{4}{5}}(y)$.
The case in which we try to approximate the area of $R_{10}^{\frac{4}{5}}$ using only five non-rectangular integration strips of equal width is depicted in the right-most panel of Figure~\ref{??}. The sides of the 
aforementioned five integration strips are depicted in Fig.~\ref{??} using dahsed lines. Taking the limit of the aformentioned sum as $n\rightarrow \infty$ results in 
Eq??, i.e. the area of $R_{10}^{\frac{4}{5}}$.

In the limit this sum approaches the area of $R_{10}^{\frac{4}{5}}$

In general can use $n$ integration strips to approximate 
the area If we are to sum together the area of  non-rectangular integration strips whose sides are translations of $b_{10}^{\frac{4}{5}}(y)$ then the result our summation would tend to
the area of $R_{10}^{\frac{4}{5}}$.

>>>>

Lets clarify the above by working through a detailed example. If we set the value of $\alpha$ to $\frac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
\begin{equation}
\int_{a_{10}^{\frac{4}{5}}(y)}^{b_{10}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
\end{equation}
Let $R_{10}^{\frac{4}{5}}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{10}^{\frac{4}{5}}(y)$. The region $R_{10}^{\frac{4}{5}}$ is depicted and labelled in the right-most panel of Figure.~\ref{??}. We are now in a position to assign a geometric 
interpretaion to Eq.~\eqref{}. We can approximate the area of $R_{10}^{\frac{4}{5}}$ by summing together the area of $n$ non-rectangular integration strips of the same width that inscribe $R_{10}^{\frac{4}{5}}$. The only resctriction being: the sides of these non-rectangualar integration strips have to be translations of $b_{10}^{\frac{4}{5}}(y)$.
Taking the limit of the aformentioned sum as $n\rightarrow \infty$ results in 
Eq??, i.e. the area of $R_{10}^{\frac{4}{5}}$. The case in which we try to approximate the area of $R_{10}^{\frac{4}{5}}$ using only five non-rectangular integration strips of equal width is depicted in the right-most panel of Figure~\ref{??}. The sides of the 
aforementioned five integration strips are depicted in Fig.~\ref{??} using dahsed lines. The analytic expressions associated with these dashed curves are contained in the set $\mathsf{B}_{10}^{\frac{4}{5}}$.

If we set the value of $\alpha$ to $\frac{4}{5}$, but we do not fix the value of $t$ then Eq.~\eqref{eq:ex1} reduces to:
\begin{equation}
\int_{a_{t}^{\frac{4}{5}}(y)}^{b_{t}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
\end{equation}
If we evaluate the above integral we obtain the area of the region $R_{t}^{\frac{4}{5}}$. The region $R_{t}^{\frac{4}{5}}$ is the region bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\frac{4}{5}}(y)$.
Note that $R_{t}^{\frac{4}{5}}$ is a function of $t$. The regions $\mathsf{R}^{\frac{4}{5}}$ are depicted in the rightmost panel of Fig\textbf{??}.

The boundaries of these regions are depicted in varying shades of gray.

We depict $R_{t}^{\frac{4}{5}}$ in the left most panel of Fig.~\textbf{??} for all $t\in\mathsf{T}$. The set of functions

If we change the value of $t$ we change the area

In general can use $n$ integration strips to approximate

the area If we are to sum together the area of  non-rectangular integration strips whose sides are translations of $b_{10}^{\frac{4}{5}}(y)$ then the result our summation would tend to
the area of $R_{10}^{\frac{4}{5}}$.
